---
title: "Possession and pace, Offensive/Defensive Ratings and the Four Factors"
#author: "Frida Gomam"
date: 2021-03-04
categories: ["R", "Basketball", "NBA"]
tags: ["Team Analysis", "Visualization", "Four Factors"]
---

```{r, echo=FALSE}
knitr::opts_chunk$set(error = TRUE)
```

The possession concept, in partiuclar the concept of equal pessessions for oppents in a game, is central to basketball analysis.Estimates of possessions have existed for approximately two
decades, but the various formulas have sometimes created confusion. I'm looking to study the relationship between poessions and various statistics using estimates to provide a common basis for future posession estimation and discussing concepts like pace and four factors between NBA teams in the ___ for the purposes of this post. 

Pace can be analyzed by calculating posessions first and the stricly related statistic accounting for the pace of the game is calculating total minutes played by all the players. 

Per-possession efficiency is measured as the poitns scored or alloed per 100 possessions, called Offensive(ORtg) and Defensive (DRtg) Rating, respectively; 

ORtg = P T ST /P OSST (2.3) DRtg = PTSO/POSSO (2.4)
where the subscripts T and O refer to whether the statistic is computed on the analyzed team or the opponent(s).

where the subscripts T and O refer to whether the statistic is computed on the analyzed team or the opponent(s).

Finally, you have your Four-Factor forumals computing for each of the offense and defense. 

```{r include = TRUE}
library(BasketballAnalyzeR)

PbP <- PbPmanipulation(PbP.BDB)
tm <- c("BOS","CLE","GSW","HOU")
selTeams <- which(Tadd$team %in% tm)

plot(FF.sel)
```

## Pace 


## Offensive/Defensive Ratings


## Offensive/Defensive Four Factors 

